\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Re-organisation of method description
Updated title and abstract

\title{\LARGE \bf
    Eye tracking with Educational Robots: A Cautionary Tale
}

@@

We present an eye-tracking study on an educational robot
Thymio II~\cite{riedo2012two} with 52 participants. The participants observed the robot
detecting obstacles in the first phase of the experiment and they
interacted with the robot in the second phase of the experiment.
Finally, they were asked to explain the functionality of the robot. The
gaze of the participants was recorded during both the phases. The values
from the robot's sensors were visualised on the robot's body using LEDs
in two different ways in the two experimental conditions and there was
no sensor data visualisation in the control condition. We found that the
sensor data visualisation has an impact on the gaze patterns and the
performance of the participants. The main goal of the experiment was to
investigate that eye tracking could bring insights to the effectiveness
of the interaction between the human user and the robot.

@@

\section{Method Application}

>>>>

\title{\LARGE \bf
    Eye-Tracking: a New Look at Human-Robot Interaction Assessment
}

@@

Eye-tracking has been previously shown to be an effective proxy to understand
complex socio-cognitive interactions. Yet its application to human-robot
interactions (HRI) remains limited. This article presents the state of the
art in eye-tracking methods for interaction assessment, and explores how those
are applicable to HRI.

Techniques based on mobile eye-tracking as well as the main analysis approaches
for eye-tracking data are first exhaustively presented, with an emphasis on
those we believe relevant to robotics. We then report on a study involving the
educational robot Thymio II~\cite{riedo2012two} with 52 participants: the
students have to explain a pre-programmed behaviour of the robot with or without
the help of visual cues. The study setup and analysis illustrate how to apply
eye-tracking techniques to actual human-robot interaction situations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Eye-tracking}

\subsubsection{Apparatus}
\begin{enumerate}
\item Stationary
\item Mobile 
\item Dual eye-tracking

\end {enumerate}

\subsubsection{Mobile Eye-tracking setup}

\begin{enumerate}
\item Calibration
\item Recording Scene 
\item Recording Gaze

\end {enumerate}

\subsubsection{Use cases for mobile eye-tracking}

\begin{enumerate}
\item Stationary target, stationary observer
\item Moving target, stationary observer
\item Stationary target, moving observer
\item Moving target, moving observer
\end{enumerate}

\subsection{Data and Analysis}

\begin{enumerate}
\item Fixaitons
\item Saccades and transitions
\item Smooth Persuite
\item Areas of Interest
\item Heatmaps

\end {enumerate}

\subsection{Joint attention and social behaviour analysis}

\section{Method Application Example}
